### 2018-12-18 Sections/models_for_quantum_computation.tex
adiabatic - written almost done, needs references 2D HLF - figure caption better explanation

\emph{}

@@

\comment{Something about universality}

>>>>

\emph{The glued-trees problem} Consider two binary trees each of depth $n$. Each tree has $2^{n+1}-1$ vertices, the two trees are randomly glued as in Fig~\ref{fig:glued_tree}). More specifically, a leaf is chosen from the left, is connected to a leaf on the right at random, which is then connected to another leaf on the left, and so on. Every leaf on the left is connected to two on the right and vice versa. This creats a random cycle that alternates between the two trees. The problem is to, starting from the left root, to find a path to the right root in the smallest possible number of steps. Classical algorithms require at least a subexponential in $n$ number of quiries, but there exists a polynomial-time quantum algorithm based on quantum walks.

@@

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.5\textwidth]{glued_tree.pdf}
	\captionspacefig \caption{A glued tree with $n=4$} \label{fig:glued_tree}
\end{figure}

The computational power of the circuit model and the adiabatic model of quantum computing are equivalent up to a polynomial overhead. In the circuit model, a set of gates is said to be universal if any unitary operation may be approximated to arbitrary accuracy by a quantum circuit involving only those gates. The analog of such a set of gates in AQC is a Hamiltonian.

A time-dependent Hamiltonian H(t) is universal if, given an arbitrary quantum circuit $U$ operating on an arbitrary multipartite initial state $\ket{\psi}$, the ground state of $H(t_f)$ is equal to $U\ket{\psi}$.

It has been proven that AQC can efficiently simulate the circuit model \cite{}, which means that it is universal for quantum computing.

### 2018-12-18 Sections/quantum_algorithms.tex
adiabatic - written almost done, needs references 2D HLF - figure caption better explanation

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.35\textwidth]{shallow_circuits_2D}
\captionspacefig \caption{\label{fig:2DHLFgrid} Implementation of the HLF problem on a 2D grid. The qubits are represented as green circles (some omitted for clarity), and CZ gates are drawn in red.\comment{Better explanation}}
\end{figure}

>>>>

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.35\textwidth]{shallow_circuits_2D}
\captionspacefig \caption{\label{fig:2DHLFgrid} Implementation of the HLF problem on a 2D grid. The qubits are represented as green circles (some omitted for clarity), and CZ gates are drawn in red.  To implement the circuit $\hat U_Q$, the qubits at the vertex of the graph $G(A)$ embedded into a 2D grid. Then $\hat U_q$ can be decomposed into a product of nearest-neighbor CZ gates and $S$.}
\end{figure}
